\title{Mauritius Muslim Matrimonial System}


\documentclass[12pt]{article}
\newcommand{\secref}[1]{Section~\ref{sec:#1}}

\begin{document}
\maketitle

\section{Overview}

The matrimonial system consists of two main parts namely:

\begin{itemize}
	\item Virtual Part
	\item Physical Part
\end{itemize}

The physical part entails the interactions between the different persons in real-life while the virtual part will only support the physical part. Both the virtual part and physical parts have financial implications such as server cost or office rent. 

The rest of this document describes the virtual part in \secref{virtualPart}, physical part in \secref{physicalPart} and financial part in \secref{financialPart}.



\section{Virtual Part}\label{sec:virtualPart}

The virtual part consist of:
\begin{itemize}
	\item Website
	\item Facebook page
\end{itemize}

In brief, the Website will be a catalog of members and is only a way to expose members' profiles and enable them to search for compatible spouses. Once a member has found a compatible spouse, s/he will contact us through the facebook page after which a Nikka Agent will take over.


\subsection{Website}
The functional requirements of the website are:
\begin{enumerate}
	\item Member can register
	\item Member should be able to provide personal description\footnote{to be defined} and potential spouse's description\footnote{to be defined}.
	\item Members only expose description
	\item Members cannot:
	\begin{itemize}
		\item communicate through message
		\item put photos
		\item put contact links (facebook profile, contact number)
	\end{itemize}
	\item Administrator should be able to remove members' profiles
\end{enumerate}

Both the personal description and potential spouse's description will include a set of predefined questions to ensure no one can put personal information that will reveal identify of the member. All members on the website should be anonymous. No members should be able to know the identify of other members by reading their profile. If a particular member is interested in a particular profile, s/he sends a message on the facebook page with the id(s) of the profile(s) 

\section{Physical Part}\label{sec:physicalPart}
The physical part includes persons having different roles and interactions between these persons. The rest of this section details the roles and interaction (workflow) in \secref{roles} and \secref{} respectively.

\subsection{Roles}\label{sec:roles}
The physical part will include persons having the following roles:
\begin{itemize}
	\item IT experts: for handling the virtual part
	\item Members: male/female looking for potential spouses
	\item Nikah agent: male/female depending on the member who acts as a broker between the members 
	\item Imams from different jamaats: in case the members wishing to marry are from different jamaats.
\end{itemize}

\subsection{Workflow}\label{sec:Workflow}

The workflow will consist of the following interaction:
\begin{itemize}
	\item Members(male/female) only search for potential spouse on the website
	\item  With interested profile in hand, they contact a  Nikah Agent
	\item  Nikah Agent communicates with the potential spouse involving family members whenever/wherever required
	\item  Nikah Agent requests photo of the members
	\item  Members are invited for a first meeting with with the Nikah Agent to discuss compatibility issues, at different time for the brother and sister
	\item  During this meeting, the photos will also be shown to the member
	\item  If they wish to continue forward, at this time, parents can be involved. From this point, if they can continue on their own, they can 
	\item  Or they can request our help depending on their requirements (fiqi advise)
\end{itemize}

\section{Financial Aspects}\label{sec:financialPart}
The complete system will be completely free. No person with a particular role can request a salary or fee for themselves. Thus, the system should be completely free and any costs will/should be subsidized by donations.

Initially, the minimum cost for the project will consists of:
\begin{itemize}
	\item Max Rs.2000 for website per month. Involve cost of website hosting, backup (already subsidized by a person)
	\item an office, can be a temporary place for meeting, anywhere in the Island. For now, office in the following location are already available:
		\begin{itemize}
			\item Vacoas
		\end{itemize}
\end{itemize}




\end{document}
